Numerical simulation of the Cordilleran ice sheet through the last glacial cycle

### 2014-06-18 cordillera-cycle.tex
Correct caption of deglacial flow directions fig.

% fig:lastflow
\begin{figure*}
  \includegraphics{lastflow}
  \caption{Modelled directions of the last basal ice velocities. Hatches
           indicate areas that remain non-sliding throughout the simulation.
           Sliding grid cells were distinguished from non-sliding grid cells
           using a velocity threshold of 1\,\unit{m\,yr^{-1}}.}
  \label{fig:lastflow}
\end{figure*}

>>>>

% fig:lastflow
\begin{figure*}
  \includegraphics{lastflow}
  \caption{Modelled directions of the deglacial basal flow velocities. Hatches
           indicate areas that remain non-sliding throughout deglaciation
           (22.0--8.0\,kyr), notably including the Interior Plateau of central
           British Columbia.
           Sliding grid cells were distinguished from non-sliding grid cells
           using a velocity threshold of 1\,\unit{m\,yr^{-1}}.}
  \label{fig:lastflow}
\end{figure*}
